func
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![R-check](https://github.com/sckott/func/workflows/R-check/badge.svg)](https://github.com/sckott/func/actions/)


`func` - tools for function development

## Installation

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("sckott/func")
```

```{r}
library('func')
```

## usage

- `func_load()`: load default parameter values for a function or vector/list of functions

```{r}
mars <- function() 5
venus <- function(z = mars(), m = list(goo = "bar"), v = function(e) e) {
  list(z, z, v)
}
mars()
venus()
z
m
v
func_load(venus)
class(z); z
class(m); m
class(v); v
```

- `func_load_path()`: same as `func_load()`, but for functions in a file

```{r}
tmpf <- tempfile(fileext=".R")
cat("myfunc <- function() 2\nfun <- function(bar = 5, zzz = myfunc()) bar + 1\n", file=tmpf)
func_load_path(path=tmpf)
bar
zzz
```


## Meta

* Please [report any issues or bugs](https://github.com/sckott/func/issues).
* License: MIT
* Please note that this project is released with a [Contributor Code of Conduct][coc].
By participating in this project you agree to abide by its terms.

[coc]: https://github.com/sckott/func/blob/master/CODE_OF_CONDUCT.md
